---
title: "R Notebook"
output: html_notebook
---
 Biostats. & Epidemi. in R. 
 Chapter 4 (Base or Tradtional Graphics)


```{r}
x <- 1:25
plot(x)
```

```{r}
xx <- c(1, 2, 3, 4, 5)
yy <- c(1, 4, 9, 16, 25)
X <- data.frame(xx, yy)
X
pairs(X)
```


coplot uses this formula: coplot(a ~ b | c + d),
This outputs scatter plots of a versus b for every joint conditioning interval of c and d.
```{r}
#a simple coplot
coplot(lat ~ long | depth, data = quakes)
```

Example of persp(x, y, z...)
```{r}
require(grDevices) #for trans3d
```
```{r}
x <- seq(-10, 10, length = 30)
y <- x
f <- function(x, y) {r <- sqrt(x^2 + y^2); 10 * sin(r)/r}
z <- outer(x, y, f)
z[is.na(z)] <- 1
op <- par(bg = "white")
persp(x, y, z, theta = 30, phi = 30, expand = 0.5, col = "lightblue")
```
```{r}
persp(x, y, z, theta = 30, phi = 30, expand = 0.5, col = "pink",
      ltheta = 120, shade = 0.75, ticktype = "detailed",
      xlab = "X", ylab = "Y", zlab = "Sinc(r)")
```

# Argugments of high-level plotting function - see page 161 in book. (or just documentation for this)
- it is possible to add legend boxs

#There are also graphic parameters that can be manipulated

#See page 168 on how to do Multiple figure outputs
-"In R, one may create an n × m  array of figures in a page, with each figure having its own margins and with the array of figures optionally surrounded by an outer margin or border. In the documentation of par{graphics}..."


# Exercises for section 4.1 
```{r}
#2 Blood pressure
bpsystolic <- c(145, 150, 135, 140, 160, 170, 138, 168, 155, 165)
diff(bpsystolic) #What this means: # In this vector, the elements are the consecutive differences of the daily measured systolic blood pressures of the patient.
mean(bpsystolic)
mean(diff(bpsystolic))
```
```{r}
#3
boxplot(145, 150, 135, 140, 160, 170, 138, 168, 155, 165)
```
```{r}
#4
calories <- c(2450, 2439, 2866, 2618)
fat.percent <- c(37.0, 36.2, 34.0, 32.1)
carb.percent <- c(43.1, 42.2, 50.0, 48.1)

# first convert  fat and carbs to number of calories
fat.cal <- c(906.5, 882.9, 974.4, 840.4) # this shows it is fluctuation

#5...just box plots!
```
```{r}
# 6 
group.midage<-c(2.5, 7.5, 13, 16.5, 17.5, 19, 22.5, 44.5, 70-5) 
accidents <- c(28, 46, 58, 20, 31, 64,149, 316, 103)

#combine these 2 parameters
age.acc <- rep(group.midage, accidents) #rep(x) replicates the values in x, 

#define breakpoints:
breakpoint <- c(0, 5, 10, 16, 17, 18, 20, 25, 60, 80) # the "bins"

#plot this as a histogram
hist(age.acc, breaks = breakpoint) #plot THIS data, using THESE bins)... diff than what's in book??
```
```{r}
#7
library(HSAUR2)
data("water", package = "HSAUR2")
water

g <- ggplot(data = water, aes(hardness, mortality)) +
  geom_point() #couldn't figure out with just plot(x)...
g

```
```{r}
plot (x = water$hardness, y = water$mortality)
abline(lm(mortality ~ hardness, data = water))
legend("topright", legend = levels(water$location), pch=c(1, 2), bty= "n")
 # just plot(water) did NOT work???? whY???? Ahhhhhh!
```
```{r}
hist(water$hardness)
```
```{r}
boxplot(water$mortality)
```

```{r}
#8
```




